---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# network.tools

<!-- badges: start -->
[![R-CMD-check](https://github.com/Pakillo/network.tools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Pakillo/network.tools/actions/workflows/R-CMD-check.yaml)
[![HitCount](https://hits.dwyl.com/Pakillo/network.tools.svg?style=flat-square)](http://hits.dwyl.com/Pakillo/network.tools)
[![HitCount](https://hits.dwyl.com/Pakillo/network.tools.svg?style=flat-square&show=unique)](http://hits.dwyl.com/Pakillo/network.tools)
<!-- badges: end -->

Tools to work with bipartite networks.

## Installation

You can install the development version of network.tools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Pakillo/network.tools")
```

## Usage

```{r }
library(network.tools)
```

### Visualise bipartite network as heatmap

```{r }
data(web)
plot_web_heatmap(web)
```

Binarize the network (make it qualitative):

```{r}
plot_web_heatmap(web, binarize = TRUE)
```

The output is a ggplot object that can be further modified:

```{r}
plot_web_heatmap(web) + viridis::scale_fill_viridis()
```


### Transform interaction data from long to wide format

```{r}
long2wide(web)
```


### Transform interaction data from wide to long format

```{r}
mat <- long2wide(web)
wide2long(mat)
```

